---
title: "final_project_api_testing"
author: "Taoli Zhen"
date: "6/3/2020"
output: html_document
---

```{r message=FALSE}
library(httr)
library(tidyverse)
library(jsonlite)
library(lubridate)
readRenviron(".Renviron")
#usethis::edit_r_environ("project")
```

# Input 
## Symbol data
```{r message=FALSE, warning=FALSE}
nasdaq <- read_csv("NASDAQ_symbols.csv")
nyse <- read_csv("NYSE_symbols.csv")
stock <- bind_rows(nasdaq, nyse)
check_symbol <- function(text){
  if (toupper(text) %in% stock$symbol){
    df = stock %>% filter(symbol == toupper(text))
    return(df)
  } else {
    #return("Sorry the symbol you enter is not found, please double check and try again.")
    return(NA)
  }
}
```

## Check input symbol
```{r}
text <- "tsla"
sn <- check_symbol(text)
is.na(sn)[1]
```


# API key for Alpha Vantage Stock API
G3O0P1B2VGOZYKZN

##TIME_SERIES_INTRADAY
```{r}
r <- GET(
  "https://www.alphavantage.co/query?function=TIME_SERIES_INTRADAY",
  query = list(
    symbol = sn$symbol,
    interval = "1min",
    outputsize = "full",
    apikey = Sys.getenv("AVS_API_KEY")
  )
)
stop_for_status(r)
json <- content(r, as = "text", encoding = "UTF-8")
df_minly <- fromJSON(json, flatten = TRUE) %>% 
  as.data.frame() %>% 
  select(symbol = ends_with("Symbol"), ends_with("close")) %>% 
  pivot_longer(
    starts_with("Time.Series.."),
    names_to = "Date",
    names_prefix = "Time.Series..1min.."
  ) %>% 
  head(390) %>% 
  mutate(Date = gsub("^.........$","", Date),
         Date = as_datetime(Date),
         Price = as.numeric(as.character(value))
         )
df_minly
```

### Graph - intraday minute closing
```{r}
ggplot(df_minly, aes(x = Date, y = Price)) +
  geom_line() +
  ggtitle(paste0("Latest Stock Prices on ", df_minly$Date[1] ," : ", sn$stock_name)) +
  theme(plot.title = element_text(lineheight = 0.7, face = "bold"))

summary(df_minly$Price)
```

## TIME_SERIES_DAILY Closing price
```{r message=FALSE}
r <- GET(
  "https://www.alphavantage.co/query?function=TIME_SERIES_DAILY",
  query = list(
    symbol = sn$symbol,
    outputsize = "full",
    apikey = Sys.getenv("AVS_API_KEY")
  )
)
stop_for_status(r)
json <- content(r, as = "text", encoding = "UTF-8")
df_daily <- fromJSON(json, flatten = TRUE) %>% 
  as.data.frame() %>%
  select(symbol = ends_with("Symbol"), ends_with("close")) %>% 
  pivot_longer(
    starts_with("Time.Series..Daily.."),
    names_to = "Date",
    names_prefix = "Time.Series..Daily.."
  ) %>% 
  separate(col = "Date", c("year", "month","date"), sep = "[.]") %>% 
  unite(col = "Date", 2:4, sep = "/") %>% 
  mutate(
    Date = gsub("^.........$","", Date),
    Date = as.Date(Date),
    Price = as.numeric(as.character(value))
    )
df_daily
```

### Graph - Past 6 months daily closing
Graph reference: https://blog.revolutionanalytics.com/2015/08/plotting-time-series-in-r.html
```{r warning=FALSE}
ggplot(df_daily %>% head(127), aes(x = Date, y = Price)) +
  geom_line() +
  ggtitle(paste0("Stock Prices for the Past 6 Months: ", sn$stock_name)) +
  theme(plot.title = element_text(lineheight = 0.7, face = "bold"))

summary(df_daily$Price %>% head(127))
```

### Graph - Past year daily closing
```{r warning=FALSE}
ggplot(df_daily %>% head(253), aes(x = Date, y = Price)) +
  geom_line() +
  ggtitle(paste0("Stock Prices for the Past Year: ", sn$stock_name)) +
  theme(plot.title = element_text(lineheight = 0.7, face = "bold"))

summary(df_daily$Price %>% head(253))
```

### Graph - historic daily closing
```{r warning=FALSE}
ggplot(df_daily, aes(x = Date, y = Price)) +
  geom_line() +
  ggtitle(paste0("Historic Stock Prices: ", sn$stock_name)) +
  theme(plot.title = element_text(lineheight = 0.7, face = "bold"))

summary(df_daily$Price)
```



## WMA 5-day daily ma for the past 90 days
```{r warning=FALSE}
r <- GET(
  "https://www.alphavantage.co/query?function=WMA",
  query = list(
    symbol = sn$symbol,
    interval = "daily",
    time_period = 5,
    series_type = "close",
    apikey = Sys.getenv("AVS_API_KEY")
  )
)
stop_for_status(r)
json <- content(r, as = "text", encoding = "UTF-8")
df_wma5 <- fromJSON(json, flatten = TRUE) %>% 
  as.data.frame() %>%
  select(symbol = ends_with("Symbol"), time_point = ends_with("Type"), starts_with("Technical.Analysis")) %>% 
  pivot_longer(
    starts_with("Technical.Analysis"),
    names_to = "ma_lag",
    names_prefix = "Technical.Analysis..WMA."
  ) %>% 
  head(91) %>% 
  separate(col = "ma_lag", c("indicator", "lag"), sep = "[.]") %>% 
  mutate(lag = replace_na(lag, "0"),
         lag = as.numeric(lag),
         value = as.numeric(as.character(value))
         )
df_wma5
```

## WMA 30-day daily ma for the past 90 days
```{r}
r <- GET(
  "https://www.alphavantage.co/query?function=WMA",
  query = list(
    symbol = sn$symbol,
    interval = "daily",
    time_period = 30,
    series_type = "close",
    apikey = "G3O0P1B2VGOZYKZN"
  )
)
stop_for_status(r)
json <- content(r, as = "text", encoding = "UTF-8")
df_wma30 <- fromJSON(json, flatten = TRUE) %>% 
  as.data.frame() %>%
  select(symbol = ends_with("Symbol"), time_point = ends_with("Type"), starts_with("Technical.Analysis")) %>% 
  pivot_longer(
    starts_with("Technical.Analysis"),
    names_to = "ma_lag",
    names_prefix = "Technical.Analysis..WMA."
  ) %>% 
  head(91) %>% 
  separate(col = "ma_lag", c("indicator", "lag"), sep = "[.]") %>% 
  mutate(lag = replace_na(lag, "0"),
         lag = as.numeric(lag),
         value = as.numeric(as.character(value))
         )
df_wma30
```

### WMA5 & WMA30 daily ma graph
```{r warning=FALSE}
ggplot(df_wma5, aes(x = lag, y = value)) +
  geom_line(aes(color = "WMA5")) +
  geom_line(data = df_wma30, aes(color = "WMA30")) +
  scale_x_reverse() +
  labs(color = "MA Days in Period") +
  ggtitle(paste0("Weighted Moving Average: ", sn$stock_name)) +
  theme(plot.title = element_text(lineheight=0.7, face="bold"))
```



## SMA 5-day daily ma for the past 90 days
```{r}
r <- GET(
  "https://www.alphavantage.co/query?function=SMA",
  query = list(
    symbol = sn$symbol,
    interval = "daily",
    time_period = 5,
    series_type = "close",
    apikey = "G3O0P1B2VGOZYKZN"
  )
)
stop_for_status(r)
json <- content(r, as = "text", encoding = "UTF-8")
df_sma5 <- fromJSON(json, flatten = TRUE) %>% 
  as.data.frame() %>%
  select(symbol = ends_with("Symbol"), time_point = ends_with("Type"), starts_with("Technical.Analysis")) %>% 
  pivot_longer(
    starts_with("Technical.Analysis"),
    names_to = "ma_lag",
    names_prefix = "Technical.Analysis..SMA."
  ) %>% 
  head(91) %>% 
  separate(col = "ma_lag", c("indicator", "lag"), sep = "[.]") %>% 
  mutate(lag = replace_na(lag, "0"),
         lag = as.numeric(lag),
         value = as.numeric(as.character(value))
         )
df_sma5
```

## SMA 30-day daily ma for the past 90 days
```{r}
r <- GET(
  "https://www.alphavantage.co/query?function=SMA",
  query = list(
    symbol = sn$symbol,
    interval = "daily",
    time_period = 30,
    series_type = "close",
    apikey = "G3O0P1B2VGOZYKZN"
  )
)
stop_for_status(r)
json <- content(r, as = "text", encoding = "UTF-8")
df_sma30 <- fromJSON(json, flatten = TRUE) %>% 
  as.data.frame() %>%
  select(symbol = ends_with("Symbol"), time_point = ends_with("Type"), starts_with("Technical.Analysis")) %>% 
  pivot_longer(
    starts_with("Technical.Analysis"),
    names_to = "ma_lag",
    names_prefix = "Technical.Analysis..SMA."
  ) %>% 
  head(91) %>% 
  separate(col = "ma_lag", c("indicator", "lag"), sep = "[.]") %>% 
    mutate(lag = replace_na(lag, "0"),
         lag = as.numeric(lag),
         value = as.numeric(as.character(value))
         )
df_sma30
```

### SMA5 & SMA30 daily ma graph
```{r warning=FALSE}
ggplot(df_sma5, aes(x = lag, y = value)) +
  geom_line(aes(color = "SMA5")) +
  geom_line(data = df_sma30, aes(color = "SMA30")) +
  scale_x_reverse() +
  labs(color = "MA Days in Period") +
  ggtitle(paste0("Simple Moving Average: ", sn$stock_name)) +
  theme(plot.title = element_text(lineheight=0.7, face="bold"))
```



## TIME_SERIES_WEEKLY Closing price
```{r message=FALSE}
r <- GET(
  "https://www.alphavantage.co/query?function=TIME_SERIES_WEEKLY",
  query = list(
    symbol = "AAPL",
    apikey = "G3O0P1B2VGOZYKZN"
  )
)
stop_for_status(r)
json <- content(r, as = "text", encoding = "UTF-8")
df_wkly <- fromJSON(json, flatten = TRUE) %>% 
  as.data.frame() %>%
  select(symbol = ends_with("Symbol"), ends_with("close")) %>% 
  pivot_longer(
    starts_with("Weekly.Time.Series."),
    names_to = "date",
    names_prefix = "Weekly.Time.Series."
  ) %>% 
  separate(col = "date", c("year", "month","date"), sep = "[.]") %>% 
  unite(col = "date", 2:4, sep = "/") %>% 
  mutate(
    date = as.Date(date),
    value = as.numeric(as.character(value))
    )
df_wkly
```

## TIME_SERIES_MONTHLY Closing price
```{r message=FALSE}
r <- GET(
  "https://www.alphavantage.co/query?function=TIME_SERIES_MONTHLY",
  query = list(
    symbol = "AAPL",
    apikey = "G3O0P1B2VGOZYKZN"
  )
)
stop_for_status(r)
json <- content(r, as = "text", encoding = "UTF-8")
df_moly <- fromJSON(json, flatten = TRUE) %>% 
  as.data.frame() %>%
  select(symbol = ends_with("Symbol"), ends_with("close")) %>% 
  pivot_longer(
    starts_with("Monthly.Time.Series."),
    names_to = "date",
    names_prefix = "Monthly.Time.Series."
  ) %>% 
  separate(col = "date", c("year", "month","date"), sep = "[.]") %>% 
  unite(col = "date", 2:4, sep = "/") %>% 
  mutate(
    date = as.Date(date),
    value = as.numeric(as.character(value))
    )
df_moly
```
